Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2018-03-18 paper.tex
mkay

Further improvements arise from using a multi-notch search to create the augmented database.
The enhanced G-PTM-D procedure employed a narrow 5 ppm tolerance around 208 mass difference notches (see supplement Supp2Calibration).
The resulting augmented database is greatly improved compared to using an open search for this step.
At this point, another advantage of the enhanced approach is clear; the overall search time dropped significantly from 22.1 hours to 2.9 hours, primarily due to the narrow tolerance multi-notch search versus the open search.

>>>>

Further improvements arise from using a multi-notch search to create the augmented database.
The enhanced G-PTM-D procedure employed a narrow 5 ppm tolerance around 208 mass difference notches (see Table S1).
The list of modifications added by G-PTM-D was generated based on a histogram of mass shifts from an open search.
Any mass shift that was confidently identified 10 or more times, was considered as a possible modification.
If a match was found in Unimod, the modification was added to our list.
The resulting augmented database is greatly improved compared to using an open search for this step.
At this point, another advantage of the enhanced approach is clear; the overall search time dropped significantly from 22.1 hours to 2.9 hours, primarily due to the narrow tolerance multi-notch search versus the open search.
